Pillar 2 - Topic Modeling

### 2019-01-21 Pillar 2 - Topic Modeling.Rmd
delete lines with sofia tuning
Ideal number of topics in LDA

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang)
```

@@

# LDA
## Fitting Model
```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

>>>>

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang)
library(ldatuning) # ideal number of topics in LDA
```

@@

# LDA

## Ideal Number of Topic

```{r, eval = FALSE}
result <- FindTopicsNumber(

  d_description_cast,
  topics = seq(from = 20, to = 150, by = 5),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = list(seed = 123),
  mc.cores = 1L,
  verbose = TRUE

)

FindTopicsNumber_plot(result1)
save(result,
     file = "LDA_ntopics.RDATA")
```

## Fitting Model
```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)
